Project 1 in reproducible research
==================================

The data given represents the activity data of a anonymous person, tracked with a unknown activity monitoring device in 2 month in 2012.

## Task 1: download and load the data

First download the data via the download function in the helper functions script
```{r}
source('helperfunctions.R')
get_download('activity.zip')
data <- read_data('./data/activity.csv')
data$Date <- as.Date(data$date, format="%Y-%m-%d")
hist(data$steps)
```

## Task 2: Calculate the mean number of steps in every day

To compute the mean number of steps per day and the sum of steps per day the data.table package is used

```{r}
library('data.table')
DT <- data.table(data)
meansteps <- DT[, mean(steps), by=Data]
sumsteps <- DT[, sum(steps), by=Date]
hist(sumsteps$V1)
plot(meansteps$Date, meansteps$V1)
```

## Task 3: What is the average daily activity pattern

## Task 4: Comparing tidy and original data

## Task 5: Differences between weekdays and weekends
